### 2018-03-10 paper/build.tex
Expand some TODOs

@@

\todo{NM}{I found terms `predicate' and `generative' hard to grasp and a bit abstract. Especially `predicate'.}

\todo{NM}{I would also like to see an actual \hs{upToDate} function for predicate, and a \hs{recover}/\hs{fetch} or something like that for generative.}

>>>>

\todo{AM}{Turn the above into a formal definition of `correctness' and add a section that provides a mathematical definition of correctness, which does not rely on materialising intermediate values.}

@@

\todo{NM}{I found terms `predicate' and `generative' hard to grasp and a bit abstract. Especially `predicate'. Let's replace it with `verifying'? And maybe `generative' with `recreating' since it allows to recreate values which were previously created by compute?}

\todo{NM}{I would also like to see an actual \hs{upToDate} function for verifying, and a \hs{recreate} for `recreating'.}

### 2018-03-10 paper/implementations.tex
Expand some TODOs

\todo{NM}{What about using shorter \hs{get} and \hs{put}? I can introduce it right in the common vocabulary, mentioning the usual get-put laws. I would also remove `get' prefixes from many functions, e.g. \hs{dependencies compute} reads fine. This is a minor issue, happy to do this at the end.}

>>>>

\todo{AM}{What about using shorter \hs{get} and \hs{put}? I can introduce it right in the common vocabulary, mentioning the usual get-put laws. I would also remove `get' prefixes from many functions, e.g. \hs{dependencies compute} reads fine. I suggest not to rush with this TODO -- let me first finish the Compute section, where many of these helper functions will be defined.}
